R Notebook

### 2024-03-04 Code/ManuscriptGenome.Rmd
Update ManuscriptGenome.Rmd

---
title: "R Notebook"
output: html_notebook
---

@@

```{r}
LightGOs <- MergedData %>% 
  separate_rows(GOs, sep = ",") %>% 
  filter(GOs %in% c("GO:0010018", "GO:0009785", "GO:0009882", "GO:0031516", "GO:0031517", "GO:0009883"))

LightKOs <- MergedData %>% 
  separate_rows(KEGG_ko, sep = ",") %>% 
  filter(KEGG_ko %in% c("ko:K02295", "ko:K12120", "ko:K12122", "ko:K12121", "ko:K12123"))
```

```{r, fig.width = 7, fig.height = 7}
MergedData %>%
  filter(!is.na(Gene_count)) %>%
  filter(PriSec == "Primary") %>%
  filter(Genus == "Prochlorococcus") %>%
  # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
  # group_by(EC) %>%
  # mutate(ECNumberTotal = sum(Gene_count)) %>%
  # ungroup() %>% View()
  # filter(ECNumberTotal != 0) %>%
  ggplot() +
  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
  facet_grid(rows = vars(Genus), scales = "free", space = "free") +
  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
  scale_x_discrete(position = "top") +
  scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
  theme_bw() +
  ggpubr::rotate_x_text(hjust = 0) 
```

```{r, fig.width = 7, fig.height = 7}
MergedData %>%
  filter(!is.na(Gene_count)) %>%
  filter(PriSec == "Primary") %>%
  # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
  # group_by(EC) %>%
  # mutate(ECNumberTotal = sum(Gene_count)) %>%
  # ungroup() %>% View()
  # filter(ECNumberTotal != 0) %>%
  ggplot() +
  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
  facet_grid(rows = vars(Genus), scales = "free", space = "free") +
  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
  scale_x_discrete(position = "top") +
  scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
  theme_bw() +
  ggpubr::rotate_x_text(hjust = 0) 
```

>>>>

---
title: "R Notebook"
---

@@

```{r}
# LightGOs <- MergedData %>% 
#   separate_rows(GOs, sep = ",") %>% 
#   filter(GOs %in% c("GO:0010018", "GO:0009785", "GO:0009882", "GO:0031516", "GO:0031517", "GO:0009883"))
# 
# LightKOs <- MergedData %>% 
#   separate_rows(KEGG_ko, sep = ",") %>% 
#   filter(KEGG_ko %in% c("ko:K02295", "ko:K12120", "ko:K12122", "ko:K12121", "ko:K12123"))
```

```{r, fig.width = 7, fig.height = 7}
# MergedData %>%
#   filter(!is.na(Gene_count)) %>%
#   filter(PriSec == "Primary") %>%
#   filter(Genus == "Prochlorococcus") %>%
#   # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
#   # group_by(EC) %>%
#   # mutate(ECNumberTotal = sum(Gene_count)) %>%
#   # ungroup() %>% View()
#   # filter(ECNumberTotal != 0) %>%
#   ggplot() +
#   geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
#   facet_grid(rows = vars(Genus), scales = "free", space = "free") +
#   scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
#   scale_x_discrete(position = "top") +
#   scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
#   theme_bw() +
#   ggpubr::rotate_x_text(hjust = 0) 
```

```{r, fig.width = 7, fig.height = 7}
# MergedData %>%
#   filter(!is.na(Gene_count)) %>%
#   filter(PriSec == "Primary") %>%
#   # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
#   # group_by(EC) %>%
#   # mutate(ECNumberTotal = sum(Gene_count)) %>%
#   # ungroup() %>% View()
#   # filter(ECNumberTotal != 0) %>%
#   ggplot() +
#   geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
#   facet_grid(rows = vars(Genus), scales = "free", space = "free") +
#   scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
#   scale_x_discrete(position = "top") +
#   scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
#   theme_bw() +
#   ggpubr::rotate_x_text(hjust = 0) 
```
